Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-20 paper.qmd
Updated the source directory

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/two_non_linear_diff_shaped_close_clusters/10_gen_rm_lg_plots.R")
```

>>>>

```{r}
#| label: std-error

# creating Standardization function
standardize = function(x){
  z <- (x - mean(x)) / sd(x)
  return( z)
}
```

```{r}
#| label: import-scripts
source("scripts/two_non_linear_diff_shaped_close_clusters/10_gen_rm_lg_plots.R")
```
